Blame and Coercion: Together Again for the Second Time

### 2019-10-18 paper.tex
make intro more friendly

There are two basic ways to represent cast space-efficiently: coercions 
\citep{herman2010space}\citep{siek2009exploring}\citep{siek2012interpretations} 
\citep{siek2015blame} and threesomes 
\citep{siek2010threesomes}\citep{garcia2013calculating}. They have different 
strength and 
weakness. \citet{garcia2013calculating} and \citet{siek2015blame} claim that 
coercion is easy to understand, but hard to implement, while threesome is easy 
to implement, but hard to understand. \citet{garcia2013calculating} in addition 
claims that coercion is more difficult to reason about formally because 
its compose function is not structurally recurisive. For instance, the 
developers of Grift \citep{kuhlenschmidt2018efficient} report that it is tricky 
to convince their proof assistants that the compose function terminates.

We present a new cast representation, hypercoercion, which has a structurally 
recursive composition. When we prove theorems about hypercoercion in Agda, the 
definition ``just works''. 
Besides, We believe hypercoercion is about as easy to understand as coercion 
because their syntax definitions are similar. For instance, the 
coercion approach represents $ 
\cOOcast{\TOOdyn}{l}{\cOOcast{\POOunit}{l'}{\TOOdyn}} $ as $ \POOunit 
?^{l} ; \POOunit\! $, while the hypercoercion approach gives $ 
\hyperCoercionC{?^l}{\POOunit}{!} $. In Section~\ref{sec:background}, we review 
coercion together with cast calculus, an intermediate languages for gradual 
typing \citep{siek2009exploring}\citep{kuhlenschmidt2018efficient}. And we 
present hypercoerion in Section~\ref{sec:hypercoercion-definition}.

@@

Many of the existing research on coercions or threesomes include proof(s) of 
correctness, that is, the cast calculus reduces to an observation ($ e 
\Downarrow o $) if and only if their calcului reduce to the same observation ($ 
e \Downarrow_{*} o $), where an observation is either a value constructor or 
blame. 
Despite the striking similarity of these proofs, they are all built from ground 
up. We present a framework for proving correctness of cast reprensentation 
(Section~\ref{sec:framework}), and use it to prove the correctness of 
hypercoercion (Section~\ref{sec:hypercoercion-correctness}). We are optimistic 
that this framework is general enough to include coercion and threesome.

Some readers might know that there are four blame strategies: $ \{Lazy, Eager\} 
\times \{D, UD\} $ \citep{siek2009exploring}. Eager strategies detect more 
potential type errors, but 
blame more programs. $ D $ and $ UD $ assign blame labels differently.
We focus on lazy strategies because recently \citet{new2019gradual} 
show that \eager{} strategies are incompatible with $\eta$-equivalence of 
functions, which suggest that they are not very ideal. 
\todo[inline]{Why do we need to explain why both LD and LUD? -KC}

>>>>

\todo[inline]{Big background}
Around 2006, many work on integrating dynamic typing and static typing emerge, 
notably gradual types \citep{siek2006gradual} and hybrid types 
\citep{flanagan2006hybrid}. The semantics of gradually typed languages is 
usuallly defined in terms of intermediate languages, where places for runtime 
type checking are explicitly stated in the forms of cast expressions. Examples 
of these intermediate languages include the blame calculus 
\citep{wadler2009well} 
and the cast calculus \citep{siek2009exploring}.
Representing casts naively, however, suffices sever space leak. 
For example, translation to intermediate languages can wrap some expressions 
with casts, including expressions at tail positions. Thus, mutually 
tail-recursive functions in source language can consume unbounded space at 
runtime. There are more examples of space leaking in \citet{herman2010space}.

\todo[inline]{The problem: space-efficient cast representation}
There are two best studied ways to represent cast space-efficiently: coercions 
\citep{herman2010space}\citep{siek2009exploring}\citep{siek2012interpretations} 
\citep{siek2015blame} and threesomes 
\citep{siek2010threesomes}\citep{garcia2013calculating}. They have different 
strength and 
weakness. \citet{garcia2013calculating} and \citet{siek2015blame} claim that 
coercion is easy to understand, but hard to implement, while threesome is easy 
to implement, but hard to understand. \citet{garcia2013calculating} in addition 
claims that coercion is more difficult to reason about formally because 
its compose function is not structurally recurisive. For instance, the 
developers of Grift \citep{kuhlenschmidt2018efficient} report that it is tricky 
to convince their proof assistants that the compose function terminates.

\todo[inline]{Our solution: hypercoercion}
We present a new cast representation, hypercoercion, which has a structurally 
recursive composition. When we prove theorems about hypercoercion in Agda, the 
definition ``just works''. 
Besides, We believe hypercoercion is about as easy to understand as coercion 
because their syntax definitions are similar. For instance, the 
coercion approach represents $ 
\cOOcast{\TOOdyn}{l}{\cOOcast{\POOunit}{l'}{\TOOdyn}} $ as $ \POOunit 
?^{l} ; \POOunit\! $, while the hypercoercion approach gives $ 
\hyperCoercionC{?^l}{\POOunit}{!} $. In Section~\ref{sec:background}, we review 
coercion together with cast calculus 
\citep{siek2009exploring}\citep{kuhlenschmidt2018efficient}. And we 
present hypercoerion in Section~\ref{sec:hypercoercion-definition}.

@@

\todo[inline]{The problem: proving correctness of cast representations}
Many of the existing research on coercions or threesomes include proof(s) of 
correctness, that is, the cast calculus reduces to an observation ($ e 
\Downarrow o $) if and only if their calcului reduce to the same observation ($ 
e \Downarrow_{*} o $), where an observation is either a value constructor or 
blame. 
Despite the striking similarity of these proofs, they are all built from ground 
up.

\todo[inline]{Our solution: a framework}
We present a framework for proving correctness of cast reprensentation 
(Section~\ref{sec:framework}), and use it to prove the correctness of 
hypercoercion (Section~\ref{sec:hypercoercion-correctness}). We are optimistic 
that this framework is general enough to include coercion and threesome.

%Some readers might know that there are four blame strategies: $ \{Lazy, 
%Eager\} 
%\times \{D, UD\} $ \citep{siek2009exploring}. Eager strategies detect more 
%potential type errors, but 
%blame more programs. $ D $ and $ UD $ assign blame labels differently.
We focus on lazy strategies because recently \citet{new2019gradual} 
show that \eager{} strategies are incompatible with $\eta$-equivalence of 
functions, which suggest that they are not very ideal. 
\todo[inline]{Why do we need to explain why both LD and LUD? -KC}
